paper_replication

### 2021-12-14 paper_replication.Rmd
Update paper_replication.Rmd

---
title: "paper_replication"
output: pdf_document
---
REPLICATION:
TODO: make sure all the counties match/are represented <- Jo
TODO: t tests for the demographic info for table 2 <- Toby
TODO: averages of averages vs. averages for table 2 
TODO: possibly email Alice asking about this county vs. state table 2 issue <- Jo 
TODO: change variable name bc it's awful <- Jo
TODO: write up <- Toby
TODO: find abortion data used by Brown et al. to compare in discussion <- Toby

>>>>

---
title: "paper_replication"
output: pdf_document
---
REPLICATION:
TODO: t tests for the demographic info for table 2 <- Toby
TODO: averages of averages vs. averages for table 2 
TODO: possibly email Alice asking about this county vs. state table 2 issue <- Jo 
TODO: write up <- Toby
TODO: find abortion data used by Brown et al. to compare in discussion <- Toby
